---
title: "Peer-graded Assignment: Course Project: Shiny Application and Reproducible Pitch"
author: "Veron SJ"
date: "7th October 2017"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, cache = TRUE, echo = FALSE, 
                      message = FALSE, warning = FALSE)
```

## Introduction

- This project was created as part of the Developing Data Products course of the Coursera [Data Science Specialisation](https://www.coursera.org/specializations/jhu-data-science).

- The app developed for the first part of the assignment demo is avalilable at: https://veronsj.shinyapps.io/datadev/

- Source code for ui.R and server.R files are available on the GitHub repo: https://github.com/vsjamilat/DevelopingDataProduct


##  Web Application functionality

The site allows users to predict the weight of a car (in 1000 lbs) given the fuel efficiency in miles per gallon (MPG).

User may choose a certain of MPG using the slider bar to get the predicted weight of a car.

Predictions are made using linear regression model. Model 1 is using MPG as the input whereas Model 2 with additional extra sline term as the input.

##  Summary of dataset used
Predictions are using the mtcars dataset from [R].

```{r, echo=FALSE}
summary(mtcars)

```

## The relationship between miles per gallon (mpg) and weight in 1000 lbs (wt) in the mtcars dataset.


```{r, echo=FALSE}

library(car)
scatterplot.matrix(~mpg+wt, data=mtcars, cex.axis=1.5)
```

